---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# forlabs

<!-- badges: start -->
[![GitHub version](https://img.shields.io/badge/Git-`r desc::desc_get_version() `-success)](https://github.com/torfason/zmisc)
[![R-CMD-check](https://github.com/torfason/forlabs/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/torfason/forlabs/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## `r desc::desc_get("Title")`

`r desc::desc_get("Description")`

## Installation

Use `pak` to install the development version of `forlabs` from
[GitHub](https://github.com/torfason/forlabs):

```r
pak::pak("torfason/forlabs")
```

## Usage

The forcats package offers an extensive suite of functions tailored for handling
factor variables effectively. This package presents a complementary set of
functions, designed specifically to operate seamlessly on haven_labelled
vectors.

The functions included in forlabs are designed to emulate the functionality of
those in forcats as closely as possible. For instance, the following
illustration uses `lbl_count()` to create a frequency table generated for a
`haven_labelled` vector of fruit, in comparison with how this can be done
with a `factor` variable using `forcats::fct_count()`:

```{r example_count}
library(forlabs)
library(forcats)

# Count the different levels of a labelled variable
lbl_count(fruit_lbl) #|> gt::gt()

# Count the different levels a factor variable
fct_count(fruit_fct) #|> gt::gt()
```

The package also offers functions for shifting and otherwise manipulating
labelled variables.

```{r}
# Veggies is indexed by prime number ...
veggies |> lbl_count() #|> gt::gt()
```

```{r}
# But can be 'densified' to be indexed by 1:n instead ...
dense_veggies <- veggies |> lbl_densify()
dense_veggies |> lbl_count() #|> gt::gt()
```

```{r}
# And shifted to run from zero instead of 1
shifted_veggies <- veggies |> lbl_shift()
shifted_veggies |> lbl_count() #|> gt::gt()  
```

```{r}
# If a variable contains unlabelled values, as is the
# case with exotic_veggies, the labels can be filled
filled_exotic_veggies <- exotic_veggies |> lbl_fill()
filled_exotic_veggies |> lbl_count() #|> gt::gt_preview(top_n=6, bottom_n=2)
```

## Dependencies

The `forlabs` package, almost by definition, depends on `labelled` and `haven`,
as these packages together define and implement the core class of labelled
variables (the `haven_labelled`) class.

As these packages depend on a number of other useful packages, including
`dplyr`, `stringr`, and `reader`, it is possible for `forlabs` to take a
dependency on those useful packages without incurring any extra installation
cost, in addition to other more lightweight packages such as `rlang`, `glue`,
`vctrs` and `tibble`.
