---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# forlabs

<!-- badges: start -->
<!-- badges: end -->

## `r desc::desc_get("Title")`

`r desc::desc_get("Description")`

## Installation

You can use `pak` to install the development version of `forlabs` from [GitHub](https://github.com/torfason/forlabs) with:

```r
pak::pak("torfason/forlabs")
```

## Usage

The many useful functions provided by `forcats` are useful for working with factors, but if the variable of interest is `labelled` rather than `factor` it is helpful to have utilities that work with them natively.

The functions in `forlabs` should be as closely comparable to those in `forcats`.

The following shows a count table for a `labelled` vector of veggies:

```{r example}
library(labelled)
library(forlabs)
## basic example code
set.seed(42)
veggie_types <- c("Broccoli" = 1, "Carrot" = 2, "Cucumber" = 3, "Potato" = 4, "Tomato" = 5)
veggies <- labelled(rbinom(20, 5, 0.7), labels = veggie_types)
lbl_count(veggies) |> gt::gt()
```

If we had a `factor` variable we would have used the parallel `forcats` function instead:

```{r}
library(forcats)
veggies_fct <- as_factor(veggies)
fct_count(veggies_fct) |> gt::gt()
```

