---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# forlabs

<!-- badges: start -->
[![R-CMD-check](https://github.com/torfason/forlabs/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/torfason/forlabs/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## `r desc::desc_get("Title")`

`r desc::desc_get("Description")`

## Installation

Use `pak` to install the development version of `forlabs` from
[GitHub](https://github.com/torfason/forlabs):

```r
pak::pak("torfason/forlabs")
```

## Usage

The forcats package offers an extensive suite of functions tailored for handling factor variables effectively. This package presents a complementary set of functions, designed specifically to operate seamlessly on haven_labelled vectors.

The functions included in forlabs are designed to emulate the functionality of those in forcats as closely as possible. For instance, the following illustration presents a frequency table generated for a `haven_labelled` vector of vegetables:

```{r example}
library(labelled)
library(forlabs)

## Generate the veggies variable, a list of 20 veggies, of five types
set.seed(42)
veggie_types <- c("Broccoli" = 1, "Carrot" = 2, "Cucumber" = 3, "Potato" = 4, "Tomato" = 5)
veggies <- labelled(rbinom(20, 5, 0.7), labels = veggie_types)

# Count the different levels
lbl_count(veggies) |> gt::gt()
```

If we had a `factor` variable we would have used the equivalent `forcats` function
instead:

```{r}
library(forcats)

# Convert veggies to factor
veggies_fct <- as_factor(veggies)

# Count the different levels
fct_count(veggies_fct) |> gt::gt()
```
